---
title: "Individual Differences and Brain Activity During Sharing Decisions"
author: "Elisa Baek"
---

In this markdown, we explore the relationship between individual differences and brain activity during sharing decisions (Sharing Task).


```{r, ECHO=FALSE}
require(lmerTest)
```

Read in the necessary files:

```{r}
mentalizing<-read.csv("data/SHARE/ROIs/mentalizing.csv")
ego_betweenness<-read.csv("data/IndividualDifferenceMeasures/ego_betweeness_groups.csv")
df_combined_ment<-merge(mentalizing,ego_betweenness,by.x=c("Scan_ID"),by.y=c("pID"))
individual_differences<-read.csv("data/IndividualDifferenceMeasures/DARPA1_Complete_Survey_Data_Scales_updated.csv")
df_combined_ment<-merge(individual_differences,df_combined_ment,by.x=c("pID"),by.y=c("Scan_ID"))
language<-read.csv("data/SHARE/LanguageAnalysis/DARPA1_Language_In_Out_LIWC.csv")

reward<-read.csv("data/SHARE/ROIs/kable_vmpfc_striatum.csv")

df_combined_reward<-merge(reward,ego_betweenness,by.x=c("Scan_ID"),by.y=c("pID"))


df_combined_reward<-merge(individual_differences,df_combined_reward,by.x=c("pID"),by.y=c("Scan_ID"))

language_id<-merge(language,individual_differences,by=c("pID"))
```

Note: We are missing post-scan written reviews from 5 participants due to various technical and time issues.

H1.2: Those with higher ego betweenness centrality will show higher activity in the mentalizing system when reading article abstracts and while making sharing decisions in the Sharing Task than those with lower ego betweenness centrality (Contrasts: Sharing conditions [broad- & narrowcasting] vs. no sharing conditions [self and topic conditions]).

Result: Not Significant

```{r}
summary(lm(SHAREvsNONSHARE_reading~ego,data=df_combined_ment))
```

H2.3: The higher a participant’s score on the resistance to peer influence and/or the lower their score on the susceptibility to peer pressure scale, the lower the activation in the mentalizing system while reading article abstracts and while making sharing decisions in Phase 2 of the Sharing Task (Contrasts: sharing vs. no sharing conditions).

Result: Not Significant

```{r}
summary(lm(SHAREvsNONSHARE_reading~spp,data=df_combined_ment))
summary(lm(SHAREvsNONSHARE_reading~rpi,data=df_combined_ment))
```

H3.3: The higher a participant’s score on the interdependence subscale of the self-construal scale, the stronger the activation in the mentalizing system and the more self-other overlap in the ventral-dorsal gradient of self/other-related MPFC activation when making sharing decisions in the Sharing Task (Contrast: Sharing vs. no sharing conditions).

Result: Not Significant (self/other gradient not tested)

```{r}
summary(lm(SHAREvsNONSHARE_reading~scs_inter,data=df_combined_ment))
```

H3.4: The higher a participant’s score on the independence subscale of the self-construal scale, the stronger the activation in the mentalizing system and the more self-other overlap in the ventral-dorsal gradient of self/other-related MPFC activation when making sharing decisions in the Sharing Task (Contrast: Sharing vs. no sharing conditions).

Result: Not Significant (self/other gradient not tested)

```{r}
summary(lm(SHAREvsNONSHARE_reading~scs_ind,data=df_combined_ment))
```

H3.7: The higher a participant’s score on the interdependence subscale of the self-construal scale, the more social words (as defined by the LIWC dictionary) the participant will use in their posts/messages for the Sharing Task (Phase 2). 

Result: Not Significant

```{r}
summary(lm(r_social~scs_inter,data=language_id))
```

H3.8: The lower a participant’s score on the independence subscale of the self-construal scale, the more social words (as defined by the LIWC dictionary) the participant will use in their posts/messages for the Sharing Task (Phase 2).

Result: Not Significant

```{r}
summary(lm(r_social~scs_ind,data=language_id))
```

H5.1: The higher a participant scores on empathy, the more activity will be found in the mentalizing system both when receiving and incorporating peer feedback in the Application Recommendation (Contrasts: peer feedback vs. no peer feedback; peer opinion different vs. peer opinion similar), and when reading and rating article abstracts in the Sharing Task (Contrasts: sharing vs. no sharing conditions). 

Result: Not Significant

```{r}
summary(lm(SHAREvsNONSHARE_reading~iri_ec,data=df_combined_ment))
```

H6.1: The higher a participant places the value of expression, the more likely they are to share articles, irrespective of the audience condition.

```{r}
#summary(lm(rating~veq,data=language_id))
```

H7.2: Those who score higher on narcissism will use more self-related language (first person singular) when writing Application reviews and Facebook messages in the Application Recommendation (Phase 3) and Sharing Tasks (Phase 2).

Result: Not Significant

```{r}
summary(lm(r_i~nar,data=language_id))
```

