---
title: "H2.3"
author: '@darpa_study_team'
date: "10/12/2017"
output: 
  github_document:
    html_preview: true
    toc: true
params:
  summary: TRUE
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(coefplot2)

```

```{r include=FALSE, ECHO=FALSE}
mentalizing<-read.csv("../data/SHARE/ROIs/mentalizing.csv")
ego_betweenness<-read.csv("../data/IndividualDifferenceMeasures/ego_betweeness_groups.csv")
df_combined_ment<-merge(mentalizing,ego_betweenness,by.x=c("Scan_ID"),by.y=c("pID"))
individual_differences<-read.csv("../data/IndividualDifferenceMeasures/DARPA1_Complete_Survey_Data_Scales_updated.csv")
df_combined_ment<-merge(individual_differences,df_combined_ment,by.x=c("pID"),by.y=c("Scan_ID"))
language<-read.csv("../data/SHARE/LanguageAnalysis/DARPA1_Language_In_Out_LIWC.csv")

reward<-read.csv("../data/SHARE/ROIs/kable_vmpfc_striatum.csv")

df_combined_reward<-merge(reward,ego_betweenness,by.x=c("Scan_ID"),by.y=c("pID"))


df_combined_reward<-merge(individual_differences,df_combined_reward,by.x=c("pID"),by.y=c("Scan_ID"))

language_id<-merge(language,individual_differences,by=c("pID"))
```



```{r, echo=FALSE}

md1 <- lm(SHAREvsNONSHARE_reading~spp,data=df_combined_ment)
md2 <- lm(SHAREvsNONSHARE_reading~rpi,data=df_combined_ment)

ctable1=coef(summary(md1))
tval1<-round(ctable1[2,3],3)
df1 <- summary(md1)$df[2]

stat_str1 <- paste0('t(',df1,')=',tval1)


ctable2=coef(summary(md2))
tval2<-round(ctable2[2,3],3)
df2 <- summary(md2)$df[2]

stat_str2 <- paste0('t(',df2,')=',tval2)
```


```{asis eval=params$summary}

## Hypothesis

```


| `r ifelse(params$summary,'Hypothesis','') ` |  `r ifelse(params$summary,'Result','') ` |
| --------------------------------------------------- | --- |
| `r ifelse(params$summary,'**H2.3**','[**H2.3**](hypotheses/H2.3.md)')`: The higher a participant’s score on the resistance to peer influence and/or the lower their score on the susceptibility to peer pressure scale, the lower the activation in the mentalizing system while reading article abstracts and while making sharing decisions in Phase 2 of the Sharing Task (Contrasts: sharing vs. no sharing conditions). | Not Significant `r paste(stat_str1,stat_str2)` |



```{asis, eval=params$summary}
## Results

### Model 1 - Resistance to peer influence

```


```{r, echo=FALSE, eval=params$summary}

md1$call

round(coeftab(md1, clevel=.95, sd=F, p.val=F),1)

coefplot2(md1)
```


```{r, echo=FALSE, eval=params$summary}
summary(md1)
```



```{asis, eval=params$summary}

### Model 2 - Susceptibility to peer pressure

```


```{r, echo=FALSE, eval=params$summary}
md2$call

round(coeftab(md2, clevel=.95, sd=F, p.val=F),1)

coefplot2(md2)
```


```{r, echo=FALSE, eval=params$summary}
summary(md2)
```
